Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-02-11 WSSSPE2_report/WSSSPE2_review.tex
Update WSSSPE2_review.tex

\todo{VOLUNTEER NEEDED to neaten this - columnize, add short intro sentence that these were generated from people who signed the google doc saying they were there and are not complete, also added names from breakout groups}

Abani Patra, Univ @ Buffalo
Alan Simpson,  EPCC, The University of Edinburgh
Aleksandra Pawlik, Software Sustainability Institute
Alice Allen, Astrophysics Source Code Library (ASCL)
Andre Luckow, Rutgers
Andy Nutter-Upham, Whitehead Institute
Anshu Dubey  Lawrence Berkeley National Laboratory
Ardita Shkurti University of Nottingham
Benjamin Pharr, University of Mississippi
Berkin Malkoc, Istanbul Technical University
Bryan Marker, The University of Texas at Austin
Carl Boettiger, UCSC/ropensci
Carol Song, Purdue University
Chris Bogart, ISR/CMU
Chris Lenhardt
Cody J Permann, Idaho National Laboratory
Colin C. Venters, University of Huddersfield
Daniel S. Katz, U Chicago \& Argonne
David Bernholdt, Oak Ridge National Laboratory
David Henty,  EPCC, The University of Edinburgh
Dirk Colbry, Michigan State University
Eric Hutton,  University of Colorado
Erin Robinson, Foundation for Earth Science 
Ethan Davis, UCAR Unidata
Ethan White, University of Florida/Utah State University
Frank L\"{o}ffler, Louisiana State University
Frank Seinstra Netherlands eScience Center
Gabrielle Allen, U Illinois
Greg Wilson  Software Carpentry
Hilmar Lapp, National Evolutionary Synthesis Center (NESCent) and Duke University
James Howison, University of Texas
James Shepherd, Rice University
James Spencer, Imperial College London
John W. Cobb
John W. Peterson, Idaho National Laboratory
Jordan Adams, Tulane University
Jory Schossau, Michigan State University
Kaitlin Thaney,  Mozilla Science Lab
Karen Cranston, NESCent
Karthik Ram, , University of California, Berkeley. Berkeley Institute for Data Science and rOpenSci
Kurt Glaesemann Pacific northwest national lab
Kyle Marcus, University of Buffalo
Marcus D. Hanwell, Kitware
Mark Schildhauer,  NCEAS, Univ. Calif, Santa Barbara
Marlon Pierce, Indiana University
Matt Jones,  University of California Santa Barbara
Matt Turk, NCSA/UIUC
Mike Rilee - NASA/GSFC, Rilee Systems Technologies - 
Nancy Wilkins-Diehr, SDSC
Neil Chue Hong, Software Sustainability Institute \& University of Edinburgh, N 
Nick Jones, New Zealand eScience Infrastructure, University of Auckland
Nicole Gasparini, Tulane University, New Orleans
Pierre-Yves Aquilanti TOTAL E\&P R\&T USA
Ray Idaszak, RENCI/UNC
Ray Plante, NCSA/University of Illinois Urbana-Champaign
Richard Littauer, MIT/University of Saarland 
Robert H. McDonald - Indiana University - Data to Insight Center/Libraries - 
Robert R Downs, CIESIN, Columbia University
Samin Ishtiaq, Microsoft Research Cambridge, UK
Sarah Harris, University of Leeds
Sol Greenspan  National Science Foundation
Stephen Piccolo,  Brigham Young University, Utah
Steven R. Brandt, Louisiana State University
Suresh Marru, Indiana University 
Sushil Prasad, Georgia State University, Atlanta 
Ted Habermann, The HDF Group
Tom Clune - NASA GSFC - 
Tom Crick, Cardiff Metropolitan University, UK
Tracy Teal Data Carpentry
Wolfgang Bangerth
Yolanda Gil, Information Sciences Institute, University of Southern California

% Names below were in the working groups but were not present in the above list

Ian Kelley 
Jakob Blomer
Justin Shi
Maxime Hughes
Mike Rilee
Nathan Weeks
Rupert Nash

>>>>

\todo{VOLUNTEER NEEDED to neaten this - alphabetize by surname, columnize, add short intro sentence that these were generated from people who signed the google doc saying they were there and are not complete, also added names from breakout groups}

Alice Allen, Astrophysics Source Code Library (ASCL)
David Bernholdt, Oak Ridge National Laboratory
Jakob Blomer
Carl Boettiger, UCSC/ropensci
Chris Bogart, ISR/CMU
Dirk Colbry, Michigan State University
Anshu Dubey  Lawrence Berkeley National Laboratory
David Henty,  EPCC, The University of Edinburgh
Maxime Hughes
Eric Hutton,  University of Colorado
Daniel S. Katz, U Chicago \& Argonne
Ian Kelley 
Chris Lenhardt
Andre Luckow, Rutgers
Berkin Malkoc, Istanbul Technical University
Bryan Marker, The University of Texas at Austin
Rupert Nash
Andy Nutter-Upham, Whitehead Institute
Abani Patra, Univ @ Buffalo
Aleksandra Pawlik, Software Sustainability Institute
Cody J Permann, Idaho National Laboratory
Benjamin Pharr, University of Mississippi
Mike Rilee
Erin Robinson, Foundation for Earth Science 
Alan Simpson,  EPCC, The University of Edinburgh
Justin Shi
Ardita Shkurti University of Nottingham
Carol Song, Purdue University
Colin C. Venters, University of Huddersfield
Nathan Weeks
Ethan White, University of Florida/Utah State University

Ethan Davis, UCAR Unidata
Frank L\"{o}ffler, Louisiana State University
Frank Seinstra Netherlands eScience Center
Gabrielle Allen, U Illinois
Greg Wilson  Software Carpentry
Hilmar Lapp, National Evolutionary Synthesis Center (NESCent) and Duke University
James Howison, University of Texas
James Shepherd, Rice University
James Spencer, Imperial College London
John W. Cobb
John W. Peterson, Idaho National Laboratory
Jordan Adams, Tulane University
Jory Schossau, Michigan State University
Kaitlin Thaney,  Mozilla Science Lab
Karen Cranston, NESCent
Karthik Ram, , University of California, Berkeley. Berkeley Institute for Data Science and rOpenSci
Kurt Glaesemann Pacific northwest national lab
Kyle Marcus, University of Buffalo
Marcus D. Hanwell, Kitware
Mark Schildhauer,  NCEAS, Univ. Calif, Santa Barbara
Marlon Pierce, Indiana University
Matt Jones,  University of California Santa Barbara
Matt Turk, NCSA/UIUC
Mike Rilee - NASA/GSFC, Rilee Systems Technologies - 
Nancy Wilkins-Diehr, SDSC
Neil Chue Hong, Software Sustainability Institute \& University of Edinburgh, N 
Nick Jones, New Zealand eScience Infrastructure, University of Auckland
Nicole Gasparini, Tulane University, New Orleans
Pierre-Yves Aquilanti TOTAL E\&P R\&T USA
Ray Idaszak, RENCI/UNC
Ray Plante, NCSA/University of Illinois Urbana-Champaign
Richard Littauer, MIT/University of Saarland 
Robert H. McDonald - Indiana University - Data to Insight Center/Libraries - 
Robert R Downs, CIESIN, Columbia University
Samin Ishtiaq, Microsoft Research Cambridge, UK
Sarah Harris, University of Leeds
Sol Greenspan  National Science Foundation
Stephen Piccolo,  Brigham Young University, Utah
Steven R. Brandt, Louisiana State University
Suresh Marru, Indiana University 
Sushil Prasad, Georgia State University, Atlanta 
Ted Habermann, The HDF Group
Tom Clune - NASA GSFC - 
Tom Crick, Cardiff Metropolitan University, UK
Tracy Teal Data Carpentry
Wolfgang Bangerth
Yolanda Gil, Information Sciences Institute, University of Southern California
